Dewlap color variation in \textit{Anolis sagrei} is maintained between habitats within islands of the West Indies

### 2020-05-24 ms/sections/figures.tex
working with tables

% Map of the West Indies
\begin{figure}[H]
    \centering
	\includegraphics[width=0.8\textwidth]{figures/map.pdf}
	\caption{Map of the West Indies with sampled islands highlighted in black.}
	\label{fig:map}
\end{figure}

% Classification accuracy of SVMs
\begin{figure}[H]
    \centering
	\includegraphics[width=\textwidth]{figures/classif_svm_pca.png}
	\caption{Distributions of classification accuracy across all SVM machines (100 replicates of 5 cross-validation bins each). The dashed line represents the density of a corresponding null binomial distribution, which would be expected under random guessing (testing sets with 20\% of the observations for each island and success probability of $1/3$). Inset plots show the corresponding average confusion matrices and represent the proportion of lizards from each habitat (columns) reassigned in each other habitat (rows), with an interpretation guide in the right panel. P-values indicate deviations of the mean classification accuracy to the expected null binomial distribution. *, P < 0.05}
	\label{fig:classif_svm_pca}
\end{figure}

% Boxplots and analyses of variance
\begin{sidewaysfigure}
    \centering
	\includegraphics[width=18cm]{figures/figure_anova.png}
	\caption{Dewlap coloration varies between habitat-types along different dimensions on different islands. (A) Boxplots show the distribution of the data for the five islands with significant differences in dewlap coloration between habitat (P-values in Fig. \ref{fig:classif_svm_pca}), along the first four principal components. We report the P-values of univariate analyses of variance conducted for each island (see Methods). Horizontal bars indicate \textit{post hoc} significant contrasts at a 0.05 error rate (see Methods). *, P < 0.05. (B) Mapping of the reflectance at various wavelengths onto the principal components. Note that PC1 largely represents brightness.}
	\label{fig:boxplots}
\end{sidewaysfigure}

>>>>

% Map of the West Indies
\begin{figure}[H]
    \centering
	\includegraphics[width=0.8\textwidth]{../maps/map.pdf}
	\caption{Map of the West Indies with sampled islands highlighted in black.}
	\label{fig:map}
\end{figure}

% Boxplots and analyses of variance
\begin{sidewaysfigure}
	\centering
	\includegraphics[width=18cm]{../analyses/07-ANOVA/figure_anova.png}
	\caption{Dewlap color variation between habitat-types across the most significant islands. (A) Mapping of reflectance at various wavelengths onto the principal components (loadings from the PCA rotation matrix). (B) Distribution of PC scores between habitats along the first four PCs on each island where significant between-habitat differences were detected using SVMs. P-values are reported for univariate ANOVA (or Kruskal-Wallis tests when applicable, see Methods). Post hoc significant differences at a 0.05 error rate are indicated with horizontal bars. *, P < 0.05.}
	\label{fig:anova}
\end{sidewaysfigure}

% Classification accuracy of SVMs
\begin{figure}[H]
    \centering
	\includegraphics[width=\textwidth]{"../analyses/04-machine learning/plots/classif_svm_pca"}
	\caption{SVM classification accuracy across islands based on principal component data. Histograms show accuracy distributions over 100 replicates for each five cross-validation bins per island. The dashed line is the density of a corresponding null binomial distribution, which would be expected under random guessing (testing sets with 20\% of the observations for each island and success probability of $1/3$). Inset plots show the corresponding average confusion matrices and represent the proportion of lizards from each habitat (columns) reassigned in each other habitat (rows), with an interpretation guide in the right panel. Binomial test P-values indicate deviations of the mean classification accuracy to the null distribution. *, P < 0.05.}
	\label{fig:classif-svm-pca}
\end{figure}

### 2020-05-24 ms/sections/methods.tex
working with tables

Reflectance curves were smoothened using the R package pavo \citep{Maia2013} as well as custom R functions (where are those?) to results into one reflectance value at each nanometer in wavelength from 300 to 700nm. Because neighboring wavelengths are highly collinear in reflectance, we reduced the dimensionality of the data using principal component analysis (PCA), as per \citet{Cuthill1999, Leal2002}. We performed PCA on each island separately and systematically retained the first four principal components (PC), which together always explained more than $88.8\%$ of the variance across islands (Table \ref{suptab:pcavariances}). PC1 explained between $40$ and $56$\% of the variance across islands; PC2 explained $17.4$--$27.9$\%; PC3 $12.7$--$17.6$\% and PC4 $4.3$--$10.5$\%. The first four PCs explained similar proportions of variance when calculated for all islands together (Table \ref{suptab:pcavariances}). PCs need not represent the same wavelengths across islands because they are fitted on different datasets. Nevertheless, PC1 was very collinear with brightness for all islands (Table \ref{suptab:brightness}). PC2 correlated highly with the red and ultraviolet ends of the spectrum, which were inversely correlated with each other (Fig. \ref{fig:boxplots}A). Higher PCs corresponded to various combinations of wavelengths. Because PC1 correlated uniformly with all wavelengths across the spectrum  we considered PC2 onwards to capture the chromatic dimensions of color space, i.e. the relative contributions of the wavelengths regardless of brightness.

@@

Our data violated the multivariate analysis of variance (MANOVA) assumption of homogeneity of covariance matrices across groups for all islands but Ragged Island (Box's M-test, \citealt{Box1949, Morrison1988}, implemented in the R package heplots, \citealt{Fox2018},  Table \ref{suptab:covariances}). We also detected within-habitat deviations from multivariate normality, primarily on Abaco, Bimini and Eleuthera (Henze-Zirkler's test, \citealt{Henze1990}, implemented in the R package MVN, \citealt{Korkmaz2014}, Table \ref{suptab:multinorm}). For these reasons and to reduce the chances of false discovery, we conducted multivariate group comparisons using support vector machines (SVMs), a model-free, nonparametric supervised machine learning technique.\\

@@

Machine learning for group comparison has become more popular in ecology and evolution in the recent years (e.g. \citet{Pigot2020}). In particular, SVMs are designed to find the best possible nonlinear boundaries between labelled groups of points in multidimensional spaces, without assumptions about the distribution of the data \citep{Cortes1995, Cristianini2000, Kim2018}. This makes them well suited to field biological data, which often violate the assumptions of classical linear modeling \citep{Kim2018} and can be, as in the case of coloration, inherently highly multivariate \citep{Cuthill1999}. The significance and robustness of a classification is assessed by training a machine to recognize differences between groups on part of the data, and using that fitted machine to predict the group-labels of data points from a testing set that were not included in the training, based solely on their multivariate coordinates. This cross-validation procedure results in a proportion of correctly classified points, or generalization accuracy score, which can be compared to that expected under random guessing using a binomial test.\\

In this study, we performed SVM classifications on each island separately. We used a standard five-fold cross-validation procedure, where the data were randomly split into five bins of approximately equal sizes, and each bin was in turn taken as the testing set while the rest was used as a training set, thus resulting in five trained machines per cross-validation. We replicated this procedure 100 times for each island to account for stochastic outcomes. We performed binomial tests to evaluate the significance of the deviations in observed mean generalization accuracy per island to null expectations under random guessing. Each training data set was downsampled to the size of its least represented habitat to ensure balanced training samples. We ensured that each habitat was represented by at least five data points in the training set. All classification analyses were repeated using the more classical linear discriminant analysis (LDA), a supervised machine learning technique finding linear boundaries that maximize the differences between groups, albeit assuming multivariate normality and homogeneity of covariance matrices \citep{Ripley1996a}. We used the R package rminer \citep{Cortez2010, Cortez2016} for SVMs, and MASS (citation) for LDAs. We used rminer's default heuristic search option to automatically tune the Gaussian kernel parameter $\sigma$ and the complexity parameter $C$ for the SVMs.\\

@@

For each island where significant differences in multivariate dewlap coloration were detected between habitats, we used multiple univariate analyses of variance (ANOVA) to identify which variables were responsible for the observed differences. We constructed our ANOVA models in two steps, as per \citet{Zuur2009}. In a first step, we accounted for heterogeneity of variances across groups by systematically comparing the goodness-of-fit of an ANOVA model estimated with ordinary least squares (OLS) with that of a model estimated with generalized least squares (GLS), which allowed one estimate of residual variance per habitat (using the R package nlme, \citealt{Pinheiro2000, Pinheiro2020}). Both models were fitted with restricted maximum likelihood (REML). Goodness-of-fit was estimated using Akaike's Information Criterion corrected for small sample sizes (AICc, from the R package MuMIn, \citealt{Barton2019}), and the estimation method yielding the lowest AICc was retained. In a second step, we re-fitted the retained model with maximum likelihood (ML) to test for the effect of habitat-type using likelihood ratio tests (LRT) between a model including a habitat-term and a null model lacking it. Significant \textit{post hoc} contrasts were assessed using Tukey's Honest Significant Difference (HSD) test whenever the OLS-model was the best fit, and pairwise Wilcoxon tests whenever there was evidence for heterogeneity of variances, and the GLS-model was the best fit.\\

We further tested the robustness of our results to non-normality. For each habitat-island combination where multivariate non-normality was detected (Table \ref{suptab:multinorm}), we assessed the univariate normality of each variable (Shapiro-Wilk's test, Table \ref{suptab:normality}) and backed our ANOVA results with nonparametric Kruskal-Wallis tests every time significant deviations were detected.\\

@@

We tested for within-island spatial autocorrelation between the geographical distances among sampling sites and their euclidean distances in multivariate color space (mean PC1 to PC4 per site, Table \ref{suptab:locations}), regardless of habitat-type. Because often only a few sites were sampled per island, we could not get meaningful results from tests using sites as units of observation. Instead, we designed a permutation test where we randomly reshuffled individual lizards across sites within islands 1,000 times each, and systematically recalculated Pearson's correlation coefficient between geographic distances (computed as geodesic distances using the R package geosphere, \citealt{Hijmans2019}) and phenotypic distances. We used the resulting null distributions of correlation coefficients to assess the significance of the observed spatial autocorrelation for each island (Table \ref{suptab:autocor}).

>>>>

Reflectance curves were smoothened using the R package pavo \citep{Maia2013} as well as custom R functions (where are those?) to results into one reflectance value at each nanometer in wavelength from 300 to 700nm. Because neighboring wavelengths are highly collinear in reflectance, we reduced the dimensionality of the data using principal component analysis (PCA), as per \citet{Cuthill1999, Leal2002}. We performed PCA on each island separately and systematically retained the first four principal components (PC), which together always explained more than $88.8\%$ of the variance across islands (Table \ref{suptab:pcavariances}). PC1 explained between $40$ and $56$\% of the variance across islands; PC2 explained $17.4$--$27.9$\%; PC3 $12.7$--$17.6$\% and PC4 $4.3$--$10.5$\%. The first four PCs explained similar proportions of variance when calculated for all islands together (Table \ref{suptab:pcavariances}). PCs need not represent the same wavelengths across islands because they are fitted on different datasets. Nevertheless, PC1 was very collinear with brightness for all islands (Figure..., Table \ref{suptab:brightness}). PC2 correlated highly with the red and ultraviolet ends of the spectrum, which were inversely correlated with each other (Fig. \ref{fig:boxplots}A). Higher PCs corresponded to various combinations of wavelengths. Because PC1 correlated uniformly with all wavelengths across the spectrum  we considered PC2 onwards to capture the chromatic dimensions of color space, i.e. the relative contributions of the wavelengths regardless of brightness.

\subsubsection*{Pooled analyses}

In addition to within-island PCA, we performed a PCA on pooled data from the whole archipelago. Explain what wavelengths mapped onto what PCs (Table suptab:pcavariances). We used this dataset to partition the variance in dewlap coloration among islands, habitats and habitats within islands, using a two-way multivariate analysis of variance (MANOVA) with an interaction term. However, because the assumptions of parametric MANOVA were violated for all islands but Ragged Island (multivariate normality and homogeneity of covariance matrices, Tables suptab:multinorm, suptab:covariance), we used a semi-parametric MANOVA instead (R package MANOVA.RM, citation), with P-values calculated from a bootstrap procedure with 1,000 iterations. We calculated the proportion of variance explained by islands, habitats and the habitat-by-island interaction using partial effect sizes $\eta^2$ on a MANOVA-approximation of the analysis (R package heplots).

@@

% move this to the previous section?

Our data violated the multivariate analysis of variance (MANOVA) assumption of homogeneity of covariance matrices across groups for all islands but Ragged Island (see previous section, \citealt{Box1949, Morrison1988}, implemented in the R package heplots, \citealt{Fox2018},  Table \ref{suptab:covariances}). We also detected within-habitat deviations from multivariate normality, primarily on Abaco, Bimini and Eleuthera (Henze-Zirkler's test, \citealt{Henze1990}, implemented in the R package MVN, \citealt{Korkmaz2014}, Table \ref{suptab:multinorm}). For these reasons and to reduce the chances of false discovery, we conducted multivariate group comparisons using support vector machines (SVMs), a model-free, nonparametric supervised machine learning technique.\\

@@

Machine learning for group comparison has become more popular in ecology and evolution in the recent years (e.g. \citet{Pigot2020}). In particular, SVMs are designed to find the best possible nonlinear boundaries between labelled groups of points in multidimensional spaces, without assumptions about the distribution of the data \citep{Cortes1995, Cristianini2000, Kim2018}. This makes them well suited to field biological data, which often violate the assumptions of classical linear modeling \citep{Kim2018} and can be, as in the case of coloration, inherently highly multivariate \citep{Cuthill1999}. First, a machine is trained to recognize differences between groups within a subset of the data called the training set. Significance of differences is then assessed by testing the accuracy of that fitted machine in predicting the group-labels of data points that were not included in the training, called a testing set, based solely on their multivariate coordinates. This cross-validation procedure results in a proportion of correctly classified points, or generalization accuracy score, which can be compared to that expected under random guessing using a binomial test.\\

In this study, we performed SVM classifications on each island separately. We used a standard five-fold cross-validation procedure, where the data were randomly split into five bins of approximately equal sizes. Each bin was in turn taken as the testing set while the rest was used as a training set, thus resulting in five trained machines per cross-validation. We replicated this procedure 100 times for each island to account for stochastic outcomes. We performed binomial tests to evaluate the significance of deviations in observed mean generalization accuracy per island to null expectations under random guessing. Each training data set was downsampled to the size of its least represented habitat to ensure balanced training samples. We ensured that each habitat was represented by at least five data points in the training set.\\

All classification analyses were repeated using the more classical linear discriminant analysis (LDA), a supervised machine learning technique finding linear boundaries that maximize the differences between groups, albeit assuming multivariate normality and homogeneity of covariance matrices \citep{Ripley1996a}. We used the R package rminer \citep{Cortez2010, Cortez2016} for SVMs, and MASS (citation) for LDAs. We used rminer's default heuristic search option to automatically tune the Gaussian kernel parameter $\sigma$ and the complexity parameter $C$ for the SVMs.\\

The same procedure was repeated on principal components from the whole archipelago (see Pooled analyses) to evaluate the significance of archipelago-wide differences in dewlap coloration across habitats.\\

All machine learning classifications performed on principal components were also repeated on the original reflectance datasets reduced to 50-nm spaced wavelengths from 300 to 700nm.\\

We conducted one-dimensional sensitivity analyses (R pacakge rminer) to determine the relative importance of the different input variables during classification where significant differences were detected, both on machines trained on principal components and machines trained on non-transformed reflectance at various wavelengths. In parallel, we conducted univariate analyses of variance to independently test the importance of different variables in between-habitat variation, on islands where the machines detected significant differences based on binomial tests (next section).

@@

For each island where significant differences in multivariate dewlap coloration were detected between habitats, we used multiple univariate analyses of variance (ANOVA) to identify which variables were responsible for the observed differences. We constructed our ANOVA models in two steps, as per \citet{Zuur2009}. In a first step, we accounted for heterogeneity of variances across groups by systematically comparing the goodness-of-fit of an ANOVA model estimated with ordinary least squares (OLS) with that of a model estimated with generalized least squares (GLS), which allowed one estimate of residual variance per habitat (using the R package nlme, \citealt{Pinheiro2000, Pinheiro2020}). Both models were fitted with restricted maximum likelihood (REML). Goodness-of-fit was estimated using Akaike's Information Criterion corrected for small sample sizes (AICc, R package MuMIn, \citealt{Barton2019}), and the estimation method yielding the lowest AICc was retained. In a second step, we re-fitted the retained model with maximum likelihood (ML) to test for the effect of habitat-type using likelihood ratio tests (LRT) between a model including a habitat-term and a null model lacking the habitat-term.\\

We tested the assumptions of the parametric ANOVA for each island included in the univariate analyses. For all islands where deviations from multivariate normality were detected in at least one habitat (Table multinorm), we assessed univariate normality for each principal component (Shapiro's test, Table normality). For skewed PCs that deviated significantly from normality, we repeated the analysis using a nonparametric Kruskal-Wallis tests. We found no multivariate outliers based on the Mahalanobis distance (package). We used the cases of better fit of the GLS model relative to the OLS model as evidence for heterogeneity of variances, which were then accounted for by the GLS approach (Table anova).\\

Significant \textit{post hoc} contrasts were assessed using Tukey's Honest Significant Difference (HSD) test whenever the assumptions of normality and homogeneity of variances was met, Dunnett's T3 method when only homogeneity of variances was violated but not normality, and Nemenyi's test when normality was violated.\\

We used the same procedure to investigate which variables, if any, were involved in archipelago-wide multivariate differences between habitats detected in our two-way MANOVA design (see Pooled analyses). However, in the first step or our model comparison procedure, we added mixed-effect equivalents of our OLS and GLS models, this time with island as a random effect. The resulting four models were compared and the best fitting variance structure was retained as explained above.

@@

We tested for within-island spatial autocorrelation between the geographical distances among sampling sites and their euclidean distances in multivariate color space (mean PC1 to PC4 per site, Table \ref{suptab:locations}), regardless of habitat-type. Because often only a few sites were sampled per island, we could not get meaningful results from tests that use sites as units of observation, such as Moran's I test. Instead, we designed a permutation test where we randomly reshuffled individual lizards across sites within islands 1,000 times each, and systematically recalculated Pearson's correlation coefficient between geographic distances (computed as geodesic distances using the R package geosphere, \citealt{Hijmans2019}) and phenotypic distances. We used the resulting null distributions of correlation coefficients to assess the significance of the observed spatial autocorrelation for each island.

\subsubsection*{Site differences}

In this study, we were interested in the minimum spatial scale at which significant differences between habitats could be detected within islands. We performed multiple pairwise nonparametric Wilcoxon tests to compare dewlap coloration between sites with different habitat-types, for each pair of habitats and each variable where significant differences were detected with our analyses of variances.

### 2020-05-24 ms/sections/results.tex
working with tables

We tested for variation in \textit{A sagrei} dewlap coloration between populations living in three characteristic habitat types across nine islands that span the West Indian range of the brown anole (Fig \ref{fig:map}, \ref{supfig:map}). We found that most of the variation in coloration partitioned between islands (semi-parametric MANOVA, modified ANOVA-type statistic (MATS) = 2009.6, P < 0.001, Fig. \ref{supfig:reflectance}, explained variance $\eta^2 = 44.3$\%, MANOVA approximation). Nonetheless, we did find evidence for differences in dewlap coloration between habitat-types, and those were mostly island-specific (habitat-by-island interaction term, MATS = 384.4, P < 0.001, explained variance $\eta^2 = 11.4$\%), leaving a small but significant portion of the variation explained by an archipelago-wide habitat effect (MATS = 42.5, P = .001, $\eta^2 = 4.8$\%).\\

The small archipelago-wide effect of habitat-type was detected for PC1, PC2 and PC3 (mixed ANOVA with island as a random effect, Table \ref{suptab:anova_pooled}), but this effect was too small for post hoc tests to find which habitats differed. Because we identified deviations from univariate normality for each group (Table \ref{suptab:norm_pooled}, but no deviations from homoskedasticity, Table \ref{suptab:}), we repeated the analysis with a Kruskal-Wallis test

SVM classifiers correctly assigned individuals to their habitat of origin based solely upon dewlap coloration on five islands: Abaco, Bimini, Cayman Brac, Little Cayman, and Long island (Fig. \ref{fig:classif_svm_pca}). An LDA approach yielded similar success rates (Fig. \ref{supfig:classif_lda_pca}), suggesting robust differences between these populations. Of the five islands, Little Cayman was the best discriminated with a mean SVM generalization success of 73.4\% (Table \ref{suptab:classif_svm_pca}). The results of the classification analyses on PCA data were very similar to results from SVMs and LDAs trained on reflectance values at 50nm-spaced wavelengths from 300 to 700nm (Fig. \ref{supfig:classif_svm_refl} and \ref{supfig:classif_lda_refl}).\\

Differentiation in dewlap coloration occurred in multiple dimensions of color space. Moreover, the differences in dewlaps between habitats were not always consistent between islands, thus, we will discuss the habitat-specific variation in dewlap coloration for each island where significant differences were detected in turn (Fig. \ref{fig:boxplots}, Table \ref{tab:anova}). Figure \ref{fig:boxplots}A provides a key to map principal component scores to the underlying wavelengths. Throughout, all reported significant differences in analyses of variance (ANOVA, Table \ref{tab:anova}) where significant deviations from normality were detected (Table \ref{suptab:normality}) were also significant in nonparametric Kruskal-Wallis tests (Table \ref{suptab:kruskal}).\\

@@

On Long Island, lizards from the coppice habitat had darker dewlaps than lizards from the other habitats (PC1, Kruskal-Wallis test accounting for the presence of one outlier with very high brightness, Fig. \ref{fig:boxplots}A, Table \ref{suptab:kruskal}). Coastal lizards had relatively more ultraviolet and less blue-green reflectance in their dewlaps (PC3). These coastal-habitat lizards also scored lower on PC4, corresponding to slightly more violet and green-yellow dewlaps, and less blue dewlaps, than the mangrove lizards on the island.\\

Sensitivity analyses on classifiers suggested an overall higher relative importance for PC2 and PC3 in determining between-group differences on Abaco, both in SVM and LDA classifiers (Fig. \ref{supfig:importance_svm_pca}, \ref{supfig:importance_lda_pca}), consistent with our ANOVA results (Fig. \ref{fig:boxplots}B). There was no strong signal of differences in relative importance among principal components on the other islands. Sensitivy analyses of SVMs trained on reflectance scores rather than principal components revealed, however, a consistently higher importance of ultraviolet reflectance in between-group differences on all islands (Fig. \ref{fig:importance_svm_refl}). This pattern was not recovered for LDAs trained on reflectance scores (Fig. \ref{fig:importance_lda_refl}). Another way to get insights into the importance of variables is to perform a single LDA on the significant islands and see what variables correlate with the LDs (on PCA and on reflectance data).\\

@@

In contrast, differences in dewlap coloration between habitats were often detected in close geographical proximity. For example, Bimini, Cayman Brac and Little Cayman were among the smallest islands in our study (Fig. \ref{supfig:map}). Besides, for pairs of habitats where significant differences in dewlap coloration were detected along some principal components, comparisons of the actual sampling sites indicate that the most detectable differences involve sites that are mostly 5-10km apart, with significant differences in PC3 detected between the beach scrub and coppice habitat at little more than 100m distance from each other on Bimini (Fig. \ref{supfig:distances}, Table \ref{suptab:distances}).\\

@@

Patterns of differentiation were inconsistent across the five most significant islands. No pattern of variation was shared by all five islands, along any dimension. Some patterns did seem more common however, such as darker dewlaps among coppice lizards (Cayman Brac, Little
Cayman, and Long Island, Fig. \ref{fig:boxplots}) or the intermediate position of coppice lizards in chromatic color space (Cayman Brac and Long Island). In other cases, patterns of differentiation were reversed from one island to another, with more ultraviolet reflecting dewlaps in mangroves than in coastal habitat on Abaco and Cayman Brac, but the opposite on Little Cayman and Long Island. Overall, it seemed that patterns of heterogeneity of variance were often driven by higher variances in coloration within beach scrub lizards (Fig. \ref{fig:boxplots}, Table \ref{tab:anova}). Yet other patterns were idiosyncratic, such as the combination of higher red and ultraviolet reflectance in coastal lizards on Little Cayman, where the rule seemed to be a negative correlation between ultraviolet and red reflectance across every other island.\\

That said, archipelago-wide differences in dewlap coloration between habitats were detected by a set of SVMs trained on data pooled from the whole archipelago, regardless of island identity, both for PCA data and reflectance scores (Fig. \ref{supfig:classif_svm_pca_pooled}, \ref{supfig:classif_svm_refl_pooled}). This pattern seemed to be driven by mangrove lizards being correctly reassigned more often than predicted by chance. Sensitivity analyses on these machines suggest a relatively small role of long wavelengths (red reflectance) in driving this pattern (Fig. \ref{supfig:importance_svm_refl_pooled}), but did not reveal strong differences between the PCs in relative importance (Fig. \ref{supfig:importance_svm_pca_pooled}).  Archipelago-wide differences were not detected by LDA classifiers at all (Fig. \ref{supfig:classif_lda_pca_pooled}, \ref{supfig:classif_lda_refl_pooled}), nor by a MANOVA (Wilk's $\lambda = 0.98$, df = 2, $F(8,920)=1.17$, P = 0.316) or a semi-parametric MANOVA-equivalent (R package MANOVA.RM, citation, Wald-type statistic (df = 8) = 12.58, parametric bootstrap with 1,000 iterations, P = 0.131, Fig. \ref{supfig:pooled}).\\

% Mention the MANOVA table somewhere
% LDA to get the importance of each variable whenever MANOVA is significant, or restrict to SVM significance ---> this could be a useful function for the package

>>>>

We tested for variation in \textit{A sagrei} dewlap coloration between populations living in three characteristic habitat types across nine islands that span the West Indian range of the brown anole (Fig \ref{fig:map}, \ref{supfig:map}). We found that most of the variation in coloration partitioned between islands (two-way semi-parametric MANOVA, modified ANOVA-type statistic (MATS) = 2009.6, P < 0.001, Fig. \ref{supfig:reflectance}, explained variance $\eta^2 = 44.3$\%, MANOVA approximation). Nonetheless, we did find evidence for differences in dewlap coloration between habitat-types, and those were mostly island-specific (habitat-by-island interaction term, MATS = 384.4, P < 0.001, explained variance $\eta^2 = 11.4$\%), leaving a small but significant portion of the variation explained by an archipelago-wide habitat effect (MATS = 42.5, P = .001, $\eta^2 = 4.8$\%).\\

The small archipelago-wide effect of habitat-type was detected for PC1, PC2 and PC3 (mixed-effect ANOVA with island as a random effect, Table \ref{suptab:anova_pooled}, backed up by KW), but this effect was too small for post hoc tests to find which habitats differed. Archipelago-wide differences in dewlap coloration between habitats were also detected by SVMs trained on pooled data regardless of island identity, both for PCA data and reflectance scores (Fig. \ref{supfig:classif_svm_pca_pooled}, \ref{supfig:classif_svm_refl_pooled}). This pattern seemed to be driven by mangrove lizards being correctly reassigned more often than predicted by chance. Sensitivity analyses on these machines suggest a relatively small role of long wavelengths (red reflectance) in driving this pattern (Fig. \ref{supfig:importance_svm_refl_pooled}), but did not reveal strong differences between the PCs in relative importance (Fig. \ref{supfig:importance_svm_pca_pooled}).  Archipelago-wide differences were not detected by LDA classifiers at all (Fig. \ref{supfig:classif_lda_pca_pooled}, \ref{supfig:classif_lda_refl_pooled}). So the difference could be in something else than means.\\

Within islands, SVM classifiers correctly assigned individuals to their habitat of origin based solely upon dewlap coloration on five islands: Abaco, Bimini, Cayman Brac, Little Cayman, and Long island (Fig. \ref{fig:classif_svm_pca}). An LDA approach yielded similar success rates (Fig. \ref{supfig:classif_lda_pca}), suggesting robust differences between these populations. Of the five islands, Little Cayman was the best discriminated with a mean SVM generalization success of 73.4\% (Table \ref{suptab:classif_svm_pca}). The results of the classification analyses on PCA data were very similar to results from SVMs and LDAs trained on reflectance values at 50nm-spaced wavelengths from 300 to 700nm (Fig. \ref{supfig:classif_svm_refl} and \ref{supfig:classif_lda_refl}).\\

Differentiation in dewlap coloration occurred in multiple dimensions of color space. Moreover, the differences in dewlaps between habitats were not always consistent between islands, thus, we will discuss the habitat-specific variation in dewlap coloration for each island where significant differences were detected in turn (Fig. \ref{fig:boxplots}, Table \ref{tab:anova}, Table KW). Figure \ref{fig:boxplots}A provides a key to map principal component scores to the underlying wavelengths.\\

@@

On Long Island, lizards from the coppice habitat had darker dewlaps than lizards from the other habitats (PC1). Coastal lizards had relatively more ultraviolet and less blue-green reflectance in their dewlaps (PC3). These coastal-habitat lizards also scored lower on PC4, corresponding to slightly more violet and green-yellow dewlaps, and less blue dewlaps, than the mangrove lizards on the island.\\

Sensitivity analyses on classifiers suggested an overall higher relative importance for PC2 and PC3 in determining between-group differences on Abaco, both in SVM and LDA classifiers (Fig. \ref{supfig:importance_svm_pca}, \ref{supfig:importance_lda_pca}), consistent with our ANOVA results (Fig. \ref{fig:boxplots}B). There was no strong signal of differences in relative importance among principal components on the other islands. Sensitivity analyses of SVMs trained on reflectance scores rather than principal components revealed, however, a consistently higher importance of ultraviolet reflectance in between-group differences on all islands (Fig. \ref{fig:importance_svm_refl}). This pattern was not recovered for LDAs trained on reflectance scores (Fig. \ref{fig:importance_lda_refl}).\\

@@

In contrast, differences in dewlap coloration between habitats were often detected in close geographical proximity. For example, Bimini, Cayman Brac and Little Cayman were among the smallest islands in our study (Fig. \ref{supfig:map}). Besides, for pairs of habitats where significant differences in dewlap coloration were detected along some principal components, comparisons of the actual sampling sites indicate that the most detectable differences involved sites that were mostly 5-10km apart. Our most extreme case of significant differences occurred for PC3 between the beach scrub site and a coppice site, separated from each other by a a few hundreds of meters at most on Bimini (Wilcoxon test, Fig. \ref{supfig:distances}, Table \ref{suptab:distances}).\\

@@

Patterns of differentiation were inconsistent across the five most significant islands. Contrasts in principal components between habitats, calculated on pooled data from the whole archipelago, were not similar, for any component, among islands (contrast figure, MANOVA, P > 0.05). No pattern of variation was shared by all five significant islands, along any dimension. Some patterns did seem more common however, such as darker dewlaps among coppice lizards (Cayman Brac, Little Cayman, and Long Island, Fig. \ref{fig:boxplots}) or the intermediate position of coppice lizards in chromatic color space (Cayman Brac and Long Island). In other cases, patterns of differentiation were reversed from one island to another, with more ultraviolet reflecting dewlaps in mangroves than in coastal habitat on Abaco and Cayman Brac, but the opposite on Little Cayman and Long Island. Overall, it seemed that patterns of heterogeneity of variance were often driven by higher variances in coloration within beach scrub lizards (Fig. \ref{fig:boxplots}, Table \ref{tab:anova}). Yet other patterns were idiosyncratic, such as the combination of higher red and ultraviolet reflectance in coastal lizards on Little Cayman, where the rule seemed to be a negative correlation between ultraviolet and red reflectance across every other island.\\
